
---
title: "Time series Jaya"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Download all libraries
```{r}
library(timeSeries)
library(tseries)
library(forecast)
library(dplyr)
library(readxl)
library(rugarch)
library(ggplot2)

```


```{r}
carbon <- read.csv("Carbon_Emissions_Futures_Historical_Data_Nov3.csv")
head(carbon)

```

Plot the time series

```{r}
co <- carbon[1040:2800,]
cps <- ts(co[,c(2)], start = c(2017,1,2), frequency = 260)
plot(cps, ylab = "Prices of Carbon emission futures")
```


```{r}
carbon$returnco  = carbon$Price /lag(carbon$Price,1) -1
carbon$lreturnco = log(1+ carbon$returnco)
head(carbon)

```

Plot the Log returns time series

```{r}
lr <- carbon[1040:2800,]
lrall <- ts(lr[,c(9)], start = c(2017,1,2), frequency = 260)
plot(lrall, ylab = "Log returns of Carbon emission futures")
```

Number of days
```{r}
length(lrall)
```


```{r}

summary(lrall)

```



```{r}
hist(lrall, main = "Histogram of Log returns of Carbon emission futures", xlab = "Log returns of Carbon emission futures")
```

Split into training and testing data

```{r}
# Data from 2017 to end of 2022 for training, and 2023 for testing
lrtspre <- ts(carbon[1040:2582,c(9)], start = c(2017,1,2), frequency = 260)
lrpre <- window(lrtspre,start = c(2017,1))
lrtspost <- ts(carbon[2583:2800,c(9)], start = c(2023,1,2), frequency = 260)
lrpost <- window(lrtspost, start = c(2023,1))
```

Plot the Log returns time series for the training data

```{r}
plot(lrpre, ylab = "Log returns of Carbon emission futures", xlab = "Year")
```


Check ACF, PACF and stationarity of the training data

```{r}
acf(lrpre)
```


```{r}
pacf(lrpre)
```

```{r}
adf.test(lrpre)
```

Develop best model of ARIMA

```{r}

automodel = auto.arima(lrpre,lambda = "auto")
summary(automodel)

```

```{r}
library(lmtest)
coeftest(automodel)
```

Choose the best MA model

```{r}
M0a <- Arima(lrpre, order = c(0,0,0))  
summary(M0a)
M0b <- Arima(lrpre, order = c(1,0,0))  
summary(M0b)
M0c <- Arima(lrpre, order = c(2,0,0))  
summary(M0c)
M1 <- Arima(lrpre, order = c(0,0,1))  
summary(M1)
M2 <- Arima(lrpre, order = c(1,0,1))  
summary(M2)
M3 <- Arima(lrpre, order = c(2,0,1))  
summary(M3)
M4 <- Arima(lrpre, order = c(0,0,2))  
summary(M4)
M5 <- Arima(lrpre, order = c(1,0,2))  
summary(M5)
M6 <- Arima(lrpre, order = c(2,0,2))  
summary(M6)
M7 <- Arima(lrpre, order = c(0,0,3))  
summary(M7)
M8 <- Arima(lrpre, order = c(0,0,4))  
summary(M8)
M9 <- Arima(lrpre, order = c(0,0,5))  
summary(M9)
```



```{r}
AIC(M0a)
AIC(M0b)
AIC(M0c)
AIC(M1)
AIC(M2)
AIC(M3)
AIC(M4)
AIC(M5)
AIC(M6)
AIC(M7)
AIC(M8)
AIC(M9)
```

```{r}
library(lmtest)
coeftest(M3)
coeftest(M4)
coeftest(M9)
```


Check residuals

```{r}
checkresiduals(M4)
```


```{r}

M4f = forecast(M4,h=length(lrpost))
colors <- c("Train" = "green", "Test" = "blue", "MA(2) Prediction" = "orange", "MA(2) Forecast" = "red")

autoplot(lrpre, series = "Train") +
  autolayer(lrpost, series = "Test") +
  theme_bw() +
  autolayer(M4f$fitted, series = "MA(2) Prediction") +
  autolayer(M4f$mean, series = "MA(2) Forecast") +
  scale_color_manual(values = colors) +
  labs(color = "Series", y = "Log returns of Carbon emission futures") 

```


Compare different EGARCH models

```{r}
garchspec1 <- ugarchspec(mean.model = list(armaOrder = c(0,2), include.mean = FALSE), 
                        variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
                        distribution.model = "sstd")
garchfit1 <- ugarchfit(data = lrpre, spec = garchspec1)
AIC1 = -2*garchfit1@fit$LLH
AIC1 
```

```{r}

garchspec2 <- ugarchspec(mean.model = list(armaOrder = c(0,2), include.mean = FALSE), 
                        variance.model = list(model = "eGARCH", garchOrder = c(1, 2)),
                        distribution.model = "sstd")
garchfit2 <- ugarchfit(data = lrpre, spec = garchspec2)
AIC2 = -2*garchfit2@fit$LLH
AIC2 
```


```{r}

garchspec3 <- ugarchspec(mean.model = list(armaOrder = c(0,2), include.mean = FALSE), 
                        variance.model = list(model = "eGARCH", garchOrder = c(2,1)),
                        distribution.model = "sstd")
garchfit3 <- ugarchfit(data = lrpre, spec = garchspec3)
AIC3 = -2*garchfit3@fit$LLH
AIC3 
```


```{r}

garchspec4 <- ugarchspec(mean.model = list(armaOrder = c(0,2)), 
                        variance.model = list(model = "eGARCH", garchOrder = c(2, 2)),
                        distribution.model = "sstd")
garchfit4 <- ugarchfit(data = lrpre, spec = garchspec4)
AIC4 = -2*garchfit4@fit$LLH
AIC4 
```

Get the estimation MA(2)-EGARCH(2,2)

```{r}
garchfit4
```

Check residuals

```{r}

par(mfrow=c(2,2))
plot(garchfit4, which=8)
plot(garchfit4, which=9)
plot(garchfit4, which=10)
plot(garchfit4, which=11)


```

Perfect fit in the training data and testing data

```{r}
lrall <- ts(carbon[1040:2800,c(9)], start = c(2017,1,2), frequency = 265)

library(fGarch)
garch_model <- garchFit(formula = ~garch(2, 2), data = lrall)
mean_model_garch <- fitted(garch_model)
n_forecast <- length(lrpost)  # Number of periods to forecast
forecast_values <- predict(garch_model, n.ahead = n_forecast)

ylim <- c(-0.15, 0.2)
plot.ts(lrall, col = "grey", ylim=ylim, xaxt = "n", xlab = "Year", ylab ="Value")
axis(1, at = time(lrall), labels = format(time(lrall)))

par(new = TRUE)
plot.ts(c(mean_model_garch[1:length(lrpre)], rep(NA, length(lrpost))), col = "green", ylim = ylim, axes = FALSE, xlab = "", ylab = "")
#lines(c(rep(NA, length(mean_model_garch)), forecast_values$meanForecast), col = "red")

# Add legend
legend("topright", legend = c("Log Returns", "Prediction MA(2)-EGARCH(2,2)"), col = c('grey', 'green'), lwd = 2)

```

```{r}

ylim <- c(-0.15, 0.2)
plot.ts(lrall, col = "grey", ylim=ylim, xaxt = "n", xlab = "Year", ylab ="Value")
axis(1, at = time(lrall), labels = format(time(lrall)))

par(new = TRUE)
plot.ts(c(mean_model_garch[1:length(lrpre)], rep(NA, length(lrpost))), col = "green", ylim = ylim, axes = FALSE, xlab = "", ylab = "")
par(new = TRUE)
plot.ts(c(rep(NA, length(lrpre)), mean_model_garch[1544:1761]), col = "red", ylim = ylim, axes = FALSE, xlab = "", ylab = "")

# Add legend
legend("topright", legend = c("Log Returns", "Prediction MA(2)-EGARCH(2,2)", "Forecast MA(2)-EGARCH(2,2)"), col = c('grey', 'green','red'), lwd = 2)

```



```{r}

mean_model_fit4 <- fitted(garchfit4)
cond_volatility4 <- sigma(garchfit4)


ylim <- c(-0.065, 0.065)
plot.ts(lrpost, col = "grey", ylim=ylim, xaxt = "n", xlab = "Year", ylab ="Value")
axis(1, at = time(lrpost), labels = format(time(lrpost)))
par(new=TRUE)
plot.ts(mean_model_fit4, col="red", ylim=ylim, axes = FALSE, xlab = "", ylab ="")
par(new=TRUE)
plot.ts(cond_volatility4, col="blue", ylim=ylim, axes = FALSE, xlab = "", ylab ="")



```